%-------------------------
% Resume in Latex
% Author - Suyash, Kunal
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}

\usepackage[normalem]{ulem} % provides "\ul" (uline) command which will break at line breaks
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}  \item\small{
    \begin{tabular*}{0.98\textwidth}[t]{
      l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r
    }
      \textbf{#1} & \textit{#2} & #3
    \end{tabular*}
  }
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Falaknaaz Shaik} % Your Name
\newcommand{\course}{Computer Science and Engineering} % Your Program
\newcommand{\roll}{Software Engineer} % Your Roll No.
\newcommand{\phone}{8341784785} % Your Phone Number
\newcommand{\emaila}{falaknaazshaik465@gmail.com} %Email 1

\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Falaknaaz shaik} \\ 
    \small \raisebox{-0.1\height}\faPhone\ +91 8341784785 ~ \href{mailto:falaknaazshaik465@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{falaknaazshaik465@gmail.com}} ~ 
    \href{https://linkedin.com/in/falaknaaz-shaik-739946216/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/falaknaaz}}  ~
    \href{https://github.com/Falaknaaz123}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/Falaknaaz}}
    \vspace{-8pt}
\end{center}
}


%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{CGPA: 9.6}
      {Rajiv Gandhi University of Knowledge Technologies, Nuzvid}{2020-24}
    \resumeSubheading
      {Pre University Course}{CGPA: 9.71}
      {Rajiv Gandhi University of Knowledge Technologies, Nuzvid}{2018-20}
    \resumeSubheading{Seconday school of education}{CGPA: 10.0}{ZP High School, Revendrapadu, Guntur Dist}{2017-18}
  \resumeSubHeadingListEnd
\vspace{-5.5mm}
%
%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Technical Intern}{}
      {Synopsys Inc, Bangalore}{July 2023 - June 2024}
      \vspace{-0.9mm}
      \resumeItemListStart
    \item{Worked on Gitlab CI/CD Automation to automate the Dev and Release Pipeline. 
    \item {Integrated PGPOOL (a middleware solution) between application and database to optimize the performance of the database queries.}
    \item{Fixed few bugs in a microservice that orchestrates the workloads using Kubernetes.}
    \item {In-depth understanding of Docker, Kubernetes, Helm, Gitlab Pipelines.}
    \resumeItemListEnd
\vspace{-1.6mm}
          \resumeSubheading
      {Web Development Intern}{}
      {Edspread}{July 2022 - Sept 2022}
      \vspace{-0.8mm}
      \resumeItemListStart
    \item{Participated in conception, design, development, implementation and deployment of web-based user interface systems.Created cross-browser, fully functional web pages using HTML and CSS.}
    \resumeItemListEnd
\vspace{-7.4mm}
  \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------------
\section{\textbf{Projects}}
\resumeSubHeadingListStart
    \resumeProject
        {\uline{Automated Attendance System}}  %Project Name
        {Python, Deep Learning, HTML, CSS, Bootstrap, Django} %Project Name, Location Name
        {\href{https://github.com/Falaknaaz123/Automated-Attendance-System}{ \faGithub { }\uline{Source Code}}}
        {} %Event Dates
      \resumeItemListStart
        \item {It is a CNN-based Automated Attendance system to automate group attendance.}
        \item {It is implemented using Python, TensorFlow, and OpenCV, achieving an accuracy rate of 95 percent on average.}
        \item {Taking a single picture of the whole class attendance will be marked for all the students.}
    \resumeItemListEnd

    \vspace{-0.9mm}
    \resumeProject
        {\href{https://netflix-clone-project-8b8b7.web.app/}{\uline{Netflix Clone}}} %Project Name
        {React , Nodejs, HTML5, JavaScript, Git, Api } %Project Name, Location Name
        {\href{https://github.com/Falaknaaz123/Netflix_Clone}{ \faGithub { }\uline{Source Code}}}
        {} %Event Dates
      \resumeItemListStart
        \item {Developed Netflix clone project that aims to mimic the basic functionalities of the popular streaming platform, Netflix, using the React library.
        }
    \resumeItemListEnd

    \vspace{-0.7mm}
    \resumeProject
        {\href{https://falaknaaz123.github.io/personal_portfolio_test/}{\uline{Personal Portfolio}}} %Project Name
        {HTML, CSS, JavaScript, Git } %Project Name, Location Name
        {\href{https://github.com/Falaknaaz123/personal_portfolio_test}{ \faGithub { }\uline{Source Code}}}
        {} %Event Dates
      \resumeItemListStart
        \item {Developed and launched a personal portfolio website showcasing my skills, projects, and achievements, demonstrating proficiency in web development and design.}
    \resumeItemListEnd

\vspace{-0.7mm}
    \resumeProject
        {\uline{Emotion Aware Music}} %Project Name
        {HTML, CSS, JavaScript, Bootstrap, Django Framework Deep Learning. } %Project Name, Location Name
        {\href{https://github.com/Falaknaaz123/Emotion-aware-music}{ \faGithub { }\uline{Source Code}}}
        {} %Event Dates
      \resumeItemListStart
        \item {Front-End for Music recommendation system takes the secret image of the user after logging in and converts the captured images into gray-scale image and they will be sent to the emotion classifier Machine Learning model which helps in predicting the emotion of the user.}
    \resumeItemListEnd
    \vspace{-1.2mm}

  \resumeSubHeadingListEnd
\vspace{-5.5mm}






%-----------Technical skills-----------------
\section{\textbf{Technical Skills and Interests}}
 \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Python, Javascript, HTML, CSS } \\
     \textbf{Web Dev Tools}{: Nodejs, VScode, Git } \\ 
     \textbf{Frameworks}{: ReactJs, Express } \\
     \textbf{Cloud/Databases}{:Docker, Kubernetes, Helm, Terraform, PostgreSQL } \\  
     
     \textbf{Relevent Coursework}{: Design and Analysis of Algorithms, Operating Systems, Object Oriented Programming, Database Management System, Software Engineering} \\ 
     \textbf{Areas of Interest}{: DevOps, Full-Stack Development \\
     \textbf{Soft Skills}{: Problem Solving, Self-Learning, Communication Skills, Adaptability} \\
    }}
 \end{itemize}


\vspace{-4.9mm}
%-----------Positions of Responsibility-----------------
\section{\textbf{Positions of Responsibility}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumePOR{Event manager, } % Position
    {RGUKT, Nuzvid} %Club,Event
    {Oct 2020 - June 2022} %Tenure Period \\
     \resumeItemListStart
        \item {Worked as an Event manager for the events like Technical fests, farewell in our University.}
         \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-5.5mm}
\resumeSubHeadingListStart
\resumePOR{NSS Volunteer, } % Position
    {RGUKT, Nuzvid} %Club,Event
    {May 2021 - May 2023}
    \hspace{5.9mm} %Tenure Period \\
     \resumeItemListStart
        \item { I have participated in NSS Special Camp for 7 days at Yanamadala Village near Nuzvid.}
        \item { As a part of camp I have participated in Swachh Bharat Abhiyan, Skill Enhancement Program.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-4.9mm}

%-----------Certifications-----------------
\section{\textbf{CERTIFICATIONS}}

    \begin{itemize}
        \item {\href{https://coursera.org/share/6cc7e0684f6e0196db7e8964649f7d52}{\hspace{0cm}\line{SQL for Data Science (Apr 2023), }}{\href{https://coursera.org/share/4c2f96db5eda7f07403dcaf53bdcbf0b}{\hspace{0cm}\line{Foundations: Data, Data, Everywhere (Mar 2023) }}
    \end{itemize}
\vspace{-2.9mm}





% %-----------Achievements-----------------
% \section{\textbf{Achievements}}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
    
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
% \resumeSubHeadingListEnd
% \vspace{-5mm}



%-------------------------------------------
\end{document}
